---
title: "Package Tutorial"
author: "Gabe Dragg"
date: "2022-11-28"
output: html_document
---

# Crab Prediction

### Installation Instructions

This package uses the data from crabs.csv. The data can be downloaded from Moodle [here](https://moodle.selu.edu/moodle/mod/resource/view.php?id=4095991&redirect=1). Download the data into the data directory, and assign it to the variable "crabs".

```{r eval=FALSE, include=TRUE}
crabs <- read.csv("data/crabs.csv")
```


```{r eval=FALSE, include=TRUE}
install.packages("project.crab.prediction")
```

```{r eval=FALSE, include=TRUE}
library(project.crab.prediction)
```

### Functions Included in the Package

#### Anova Function
The anova function performs a statistical test using variance to determine if there is a significant difference between body depth and the sex in crabs. This is a useful function because it helps to determine if sex predicts body depth in crabs.

Example
```{r eval=FALSE, include=TRUE}
anova_crabs(file.path)
```

#### Jitterplot Function
The jitterplot function plots sex against body depth in crabs. The purpose of this function is to provide a visual representation of the relationship between body depth and sex in crabs.

Example
```{r eval=FALSE, include=TRUE}
crab_plot(file.path)
```

#### Column Rename Function
The column rename function renames the "body_depth" column to "crab_body_depth" which provides use because it gives a more descriptive name.

Example
```{r eval=FALSE, include=TRUE}
crab_col(file.path)
```

